Temporal Distinctiveness in Task Switching: Assessing the Mixture-Distribution Assumption --- Revision 1

### 2016-01-20 Temporal Distinctiveness & Mixture Distributions/Revision 1/Manuscript Files/main.tex
folder re-structure

%%%--------------------------------------------------------------------------------------------
\documentclass[a4paper, jou, natbib]{apa6}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes} 
\usepackage{etoolbox}

\newtoggle{jou}
\toggletrue{jou}
%\togglefalse{jou}

%\usepackage{lineno}

\title{Temporal Distinctiveness in Task Switching: Assessing the Mixture-Distribution Assumption}
\shorttitle{Mixture Distribution Assumption}
\author{James A. Grange}
\affiliation{School of Psychology, Keele University, UK}

@@

\authornote{Please address correspondence to James A. Grange, School of Psychology, Dorothy Hodgkin Building, Keele University, Keele, UK, ST5 5BG. Email: grange.jim@gmail.com. I am grateful to Chris Donkin for discussion regarding the Linear Ballistic Accumulator model. All raw data, analysis code, and model code are available to download at http://bit.ly/1l22EUV.}

@@

Evidence from the task switching paradigm has provided several lines of evidence suggesting that activation levels of task-sets decay passively as a function of time. For example, \cite{Meiran2000a} varied the temporal separation between successive tasks via the response--cue interval (RCI), the time between the response to one task and the onset of the cue for the next task. These authors reported reduced switch costs at longer RCIs; this finding is in perfect accord with a decay account for two reasons: first, on task repetition trials, the previous task's activation will have had more time to decay at longer RCIs, meaning its ability to prime performance on the current trial will have reduced (leading to slower RTs); secondly, on task switch trials, the activation levels of the previous (now irrelevant) task-set will have decayed, inducing less proactive interference on the current trial (thus resulting in faster RTs). The net result is a reduced switch cost.

However, this decay account was recently challenged by \cite{Horoufchin2011a} who manipulated RCI on a trial-to-trial basis between a short- (e.g., 50milliseconds, ms) and a long-RCI (1,000ms); they found that the reduction of switch cost was not a function of \emph{absolute} time of the RCI (e.g., between the previous trial n--1 and the current cue at n), but rather was a function of the ratio of the current RCI to that from the previous trial (between trials n--2 and n--1). Specifically, the switch cost was only reduced at longer RCIs when the previous RCI was short; when the previous RCI was also long, switch costs were not reduced. These effects were primarily localised to task repetition RT; task switch RT was not influenced by RCI or the RCI-ratio.

\cite{Horoufchin2011a} proposed these findings supported an \emph{interference} account of RCI effects, and were not compatible with a decay account. Relating to a temporal ratio model of serial memory \citep[SIMPLE][]{Brown2007}, the authors suggested that when presented with a cue on the current trial, the cognitive system engages in a retrieval attempt of the previous episodic memory trace of this task; such retrieval attempts have been shown by \cite{Brown2007} to be influenced by the \emph{temporal distinctiveness} (TD) of the episodic trace. TD refers to the degree to which the targeted episodic trace is distinguishable in memory from competing memory traces presented within a similar time-window to that of the target trace. Traces that are clustered closely in episodic memory will not be distinguishable, and thus have low TD and will have low probability to be retrieved. The sequential varying of the RCI was suggested to affect the TD of the targeted episodic trace in memory. TD is operationalised in relation to the RCI-ratio, which is the ratio of the RCI(n--2:n--1) / RCI(n--1:current trial). See Figure \ref{fig:tdAccount} for how various RCI-ratios are calculated.

\begin{figure} 
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/tdAccount.pdf}
\caption{Various manipulations of temporal distinctiveness as used by \cite{Horoufchin2011, Horoufchin2011a}. Task instances are represented by circles, and time runs from left to right. The current trial's cue is represented by the far-right circle; the episodic trace of the previous task is the middle circle, and the episodic trace of the task from two trials ago is the far-left circle. The RCI between each trace is shown for each row. The ratio is calculated as RCI(n--2:n--1) / RCI(n--1:current trial). See text for more details.}
\label{fig:tdAccount}
\end{center}
\end{figure}

When RCI-ratio is high, so too is TD, which means there is a high probability the episodic trace can be retrieved; successful retrieval primes performance, leading to a fast RT. When the RCI-ratio is low, so too is TD, which lowers the probability of successful retrieval. When retrieval fails, the task must be performed via a slower, algorithmic route, leading to a slower RT \citep[see][for a similar proposal]{Logan2002}. Intermediate RCI-ratios lead to intermediate levels of TD; therefore, a proportion of these trials will have successful retrieval, and some trials will have failed retrieval.

Figure \ref{fig:grangeData} represents a portion of data reported by \cite{Grangeinrevision}---a brief overview of the pertinent method details and analysis are presented in Appendix A---that replicates the main findings from \cite{Horoufchin2011a}; focussing on repetition RTs, increasing RCI from 50ms to 1,000ms has negligible effect on RTs when the RCI was the same as the previous trial (e.g., these data points relate to D and C in Figure \ref{fig:tdAccount}); this is because both of these conditions have an identical RCI-ratio of 1, and hence have the same TD. RCI has a considerable effect on repetition RT when the RCI has changed from the previous trial: RT is very fast when the RCI is 50ms, as this condition has a very high RCI-ratio, hence high TD (Figure \ref{fig:tdAccount} A); RT is very slow when the RCI is 1,000ms, as this condition has a very low RCI-ratio, hence low TD (Figure \ref{fig:tdAccount} B).

\iftoggle{jou}{
\begin{figure}
\begin{center}
\includegraphics[width = 0.5\textwidth]{Images/grangeData.pdf}
\caption{Data from \cite{Grangeinrevision} showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial. Error bars denote  +/- 1 standard error around the mean.}
\label{fig:grangeData}
\end{center}
\end{figure}
}{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/grangeData.pdf}
\caption{Data from \cite{Grangeinrevision} showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial. Error bars denote  +/- 1 standard error around the mean.}
\label{fig:grangeData}
\end{center}
\end{figure}
}

@@

I approach this assessment in two ways. In the first, I use a statistical test---the fixed-point property test---to assess the presence/absence of evidence for intermediate RCI-ratios being a mixture of a fast and a slow distribution. Then, in a next step I extend the model of \cite{Grange2015} to predict whole RT-distributions, which allows a direct test of the mixture-distribution assumption.
%%%--------------------------------------------------------------------------------------------

%%%--------------------------------------------------------------------------------------------
\section{Assessing the Presence of Mixture-Distributions}
\cite{VanMaanen2014} introduced a method---the ``fixed-point'' property test---for statistically testing the presence of a mixture-distribution, given two ``base'' distributions. If distribution $z$ is a mixture of two base distributions $x$ and $y$, then the fixed-point property states that the probability density for distribution $z$, $f_{z}$, is a weighted sum of the probability densities of the other two distributions $f_{x}$ and $f_{y}$. Put simply, this implies that there exists a particular response time $t$ for which the probability of providing such as response is identical for all three distributions; that is $f_{x}(t)$ = $f_{z}(t)$ = $f_{y}(t)$.

@@

\iftoggle{jou}{
\begin{figure}
\begin{center}
\includegraphics[width = 0.5\textwidth]{Images/fpExample.pdf}
\caption{Example of the fixed-point property in three distributions. Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7. The left panel shows the probability densities for each distribution. The right panel shows the density difference between different density functions. The distributions share a common crossing point at about 0.850 seconds.}
\label{fig:fpExample}
\end{center}
\end{figure}
}{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/fpExample.pdf}
\caption{Example of the fixed-point property in three distributions. Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7. The left panel shows the probability densities for each distribution. The right panel shows the density difference between different density functions. The distributions share a common crossing point at about 0.850 seconds.}
\label{fig:fpExample}
\end{center}
\end{figure}
}

@@

%%----------
\subsection{Application to the Data}
The task repetition data from Figure \ref{fig:grangeData} was assessed for the presence of a fixed-point property. In this test, the RCI-ratio of 20 can be considered the ``fast'' distribution, and the RCI-ratio of 0.05 can be considered the ``slow'' distribution. The critical question is whether intermediate RCI-ratios of 1 are a mixture of the fast and the slow distribution.

Data were trimmed before testing. Correct RTs were trimmed to retain RTs slower than 150 milliseconds, and RTs faster than 2.5 standard deviations above each subjects' mean RT. The data was then assessed for the presence of a fixed-point by passing it to the \texttt{fp} function provided in the form of \texttt{R} code from \citet{VanMaanen2014}. Visual representation of the fixed-point assessment is shown in Figure \ref{fig:mixtureDistributionData}.

\begin{figure*}
\begin{center}
\includegraphics[width = \textwidth]{Images/mixtureDistributionData.pdf}
\caption{Test of the fixed-point property in three distributions from \cite{Grangeinrevision}. The left panel shows the individual density functions for each condition of RCI-ratio (1 = 0.05, 2 = 1, 3 = 20). The middle panel shows ``crossing points'': the subtraction of pairs of density functions (indicated in legend). The right panel shows box-plots for the distribution of crossing points for individual participants in the study.}
\label{fig:mixtureDistributionData}
\end{center}
\end{figure*}

As shown in the left and center panels of Figure \ref{fig:mixtureDistributionData}, the three RT distribution functions share a common crossing point at just over 1 second. The right panel of Figure \ref{fig:mixtureDistributionData} shows box-plots of the distribution of crossing points for each pair for all subjects. There is considerable overlap in the box-plots suggesting no difference between condition pairs of crossing point (supporting the fixed-point property). Together, this visual inspection provides good evidence that the RCI-ratio = 1 RT function is a weighted mixture of the ``slow'' RT distribution (where RCI-ratio = 0.05) and the ``fast'' RT distribution (where RCI-ratio = 20), as predicted by the temporal distinctiveness model \citep{Grange2015}.

@@

\iftoggle{jou}{
\begin{figure}
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/modelOverview.pdf}
\caption{Overview of the retrieval processes in the model.}
\label{fig:modelOverview}
\end{center}
\end{figure}
}{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/modelOverview.pdf}
\caption{Overview of the retrieval processes in the model.}
\label{fig:modelOverview}
\end{center}
\end{figure}
}

@@

\cite{Grange2015} used the full mathematics of SIMPLE to obtain $p$(retrieved). To reduce the number of free parameters, in the current model $p$(retrieved) was treated as a ``semi-fixed'' parameter. To achieve this, the RCI-ratio was calculated for each RCI-sequence condition in Figure \ref{fig:grangeData}. Specifically, the RCI-ratio was 20 for n--2 to n--1 RCIs of 50ms--1000ms; the ratio was 1 for RCIs of 1000ms--1000ms and 50ms--50ms; and the ratio was 0.05 for RCIs of 50ms--1,000ms. $p$(retrieved) was ``semi-fixed'' in the sense that it was fixed at $p$(retrieved) = 1 for ratios of 20 (i.e., perfect retrieval) and fixed at $p$(retrieved) = 0 for ratios of 0.05 (i.e., failed retrieval); $p$(retrieved) was free to vary for ratios of 1. Thus, $p$(retrieved) controls the relative contribution of the two RT distributions for intermediate RCI ratios.

@@

The model was fitted to the data via a version of Quantile Maximum Probability Estimation \citep[QMPE][]{Heathcote2002}, where the model is fit to RT quantiles rather than individual RTs as per maximum likelihood (see Appendix C for details). This method was used due to the relatively low number of trials per subject, and the rather low error rate. The fits of the model to the behavioural data are shown in Figure \ref{fig:modelFit}. The best-fitting parameters are shown in Table \ref{tab:bestParameters}.

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{Best fitting model parameters from the fit routine. Note that $p$(retrieved) refers to the probability of sampling from the fast distribution only for ratio = 1 data points. See text for details.}
    \begin{tabular}{rr}
    \toprule
    Model Parameter & Value \\
    \midrule
    $p(retrieved)$     & 0.759 \\
    $A$     & 718.14 \\
    $b_{Fast}$ & 114.58 \\
    $b_{Slow}$ & 179.96 \\
    $v_{Fast}$ & 1.132 \\
    $v_{Slow}$ & 0.893 \\
    $s$     & 0.44 \\
    $ter$   & 346.42 \\
    \bottomrule
    \end{tabular}%
  \label{tab:bestParameters}%
\end{table}%

\begin{figure*}
\begin{center}
\includegraphics[width = \textwidth]{Images/qmp2RCI_drift_+_b.pdf}
\caption{Defective cumulative distribution functions for the behavioural data and the model fit for all RCI-ratios (0.05, 1, \& 20) for correct and error RT distributions.}
\label{fig:modelFit}
\end{center}
\end{figure*}

This Figure presents so-called ``defective'' cumulative distribution functions (CDFs). The data are sorted from fastest to slowest, and then quantile cut-off points are calculated for each subject according to a pre-specified set of quantiles $\vec{Q}$ (here $\vec{Q}$ = 0.1, 0.3, 0.5, 0.7, 0.9). The Figure plots the average RT for each quantile across subjects against the quantile value. The plot is a defective CDF in the sense that it also displays information about errors. Specifically, RT is plotted against $\vec{Q}$ $\times$ mean accuracy rather than just $\vec{Q}$. Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{Q}$ $\times$ (1 - mean accuracy).

The model fit to correct RT distributions is rather good. The model captures all of the main trends in the data: RT becomes facilitated as $p$(retrieved) increases (from left-to-right $p$(retrieved) = 0, $p$(retrieved) = 0.759, and $p$(retrieved) = 1). This improvement in RT is largely at the slower end of the RT distribution. Also, the defective CDFs become steeper as $p$(retrieved) is increased, reflecting generally better accuracy. Importantly, the central plot shows a good fit of the model to the data, providing support that intermediate TDs are a mixture of two base distributions.

The fit to the error RT distributions is not as good as for the correct RT distributions. However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 80\% accuracy, and average accuracy was much higher). So, there were often few error RTs per quantile bin during the model fit, making accurate estimation difficult. However, despite the poor quantitative fit, the qualitative pattern seen in the behavioural data is generally reproduced: error RT becomes generally faster and less variable as ratio increases.

@@

\section{Conclusion}
The present paper sought to assess the evidence in favour of a key prediction of the TD hypothesis of RCI effects in task switching, namely that RTs are a mixture of only one of two processes. In sum, this paper has provided good support for the TD prediction, which provides more support for these theoretical accounts \citep{Grange2015, Horoufchin2011, Horoufchin2011a}. This presents an important challenge to models of cognitive control during task switching which assume control systems work to prevent relevant task-sets decaying. Instead, loss of retrieval of task-sets appears to be well-explained by interference effects rather than time-based decay.

@@

%%%--------------------------------------------------------------------------------------------
\appendix
\section{Method and Results \citep{Grangeinrevision}}
The data presented in Figure \ref{fig:grangeData} presents a portion of the overall data presented by \cite{Grangeinrevision}. Speficially, this data comes from the ``categorisation'' condition. In this condition, 25 participants were presented with a 2x2 square grid. Two arrow cues either pointed up and down (presented above and below the grid, respectively) or left and right (presented to the left and to the right of the grid, respectively). 100ms later, a stimulus appeared in one of the grid's cells. The stimulus could be an A or a 4, presented in either red or blue font. If the arrows pointed up and down, the participants had to judge whether the stimulus was an A or a 4; if the arrows pointed left and right, the participants had to judge whether the stimulus was red or blue. Participants responded using the ``1'' and the ``9'' keys on the numerical part of the keyboard; 1 corresponded to ``letter'' and ``red'' responses, and 9 corresponded to ``number'' and ``blue'' responses. Once a response was registered, the grid was cleared for an RCI of either 50ms or 1,000ms (chosen randomly). The next task was chosen randomly. In total, participants were presented with 6 blocks of 64 trials, preceded by 16 practice trials.

@@

As we are only considering the similarity between two items ($i$ and $j$), and as an item's similarity to iself is 1, Equation \ref{eq:simpleDiscriminationA} becomes

>>>>

%%%--------------------------------------------------------------------------------------------
\documentclass[a4paper, man, natbib]{apa6}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes} 
\usepackage{etoolbox}

% \newtoggle{jou}
% \toggletrue{jou}
% \togglefalse{jou}

\usepackage{lineno}
\linenumbers

\title{Temporal Distinctiveness in Task Switching: Assessing the Mixture-Distribution Assumption --- Revision 1}
\shorttitle{Mixture Distribution Assumption}
\author{James A. Grange}
\affiliation{School of Psychology, Keele University, UK}

@@

\authornote{Please address correspondence to James A. Grange, School of Psychology, Dorothy Hodgkin Building, Keele University, Keele, UK, ST5 5BG. Email: grange.jim@gmail.com. I am grateful to Chris Donkin for discussion regarding the Linear Ballistic Accumulator model. All raw data, analysis code, and model code are available to download at http://bit.ly/1YumV7i.}

@@

Evidence from the task switching paradigm has provided several lines of evidence suggesting that activation levels of task-sets decay passively as a function of time. For example, \cite{Meiran2000a} varied the temporal separation between successive tasks via the response--cue interval (RCI), the time between the response to one task and the onset of the cue for the next task. These authors reported reduced switch costs at longer RCIs; this finding is in perfect accord with a decay account for two reasons: first, on task repetition trials, the previous task's activation will have had more time to decay at longer RCIs, meaning its ability to prime performance on the current trial will have reduced (leading to slower RTs); secondly, on task switch trials, the activation levels of the previous (now irrelevant) task-set will have decayed, inducing less proactive interference on the current trial (thus resulting in faster RTs). The net result is a reduced switch cost. \jg{It should be noted that several studies have found task repetition RTs slow as a function of RCI, the evidence for the predicted speeding of switch RT is less clear. In fact, several studies have found no evidence for RCI affecting switch RTs in the predicted direction \citep{Altmann2005, Horoufchin2011a, Meiran2000a}. However, slowing of repetition RTs with increasing RCI remains an important finding supporting decay accounts.}

However, this decay account was recently challenged by \cite{Horoufchin2011a} who manipulated RCI on a trial-to-trial basis between a short- (e.g., 50milliseconds, ms) and a long-RCI (1000ms); they found that the reduction of switch cost was not a function of \emph{absolute} time of the RCI (e.g., between the previous trial n--1 and the current cue at n), but rather was a function of the ratio of the current RCI to that from the previous trial (between trials n--2 and n--1). Specifically, the switch cost was only reduced at longer RCIs when the previous RCI was short; when the previous RCI was also long, switch costs were not reduced. These effects were primarily localised to task repetition RT; task switch RT was not influenced by RCI or the RCI-ratio.

\cite{Horoufchin2011a} proposed these findings supported an \emph{interference} account of RCI effects, and were not compatible with a decay account. Relating to a temporal ratio model of serial memory \citep[SIMPLE][]{Brown2007}, the authors suggested that when presented with a cue on the current trial, the cognitive system engages in a retrieval attempt of the previous episodic memory trace of \jg{the task-set associated with this cue}; such retrieval attempts have been shown by \cite{Brown2007} to be influenced by the \emph{temporal distinctiveness} (TD) of the episodic trace. TD refers to the degree to which the targeted episodic trace is distinguishable in memory from competing memory traces presented within a similar time-window to that of the target trace. Traces that are clustered closely in episodic memory will not be distinguishable, and thus have low TD and will have low probability to be retrieved. The sequential varying of the RCI was suggested to affect the TD of the targeted episodic trace \jg{of the task-set} in memory. TD is operationalised in relation to the RCI-ratio, which is the ratio of the RCI(n--2:n--1) / RCI(n--1:current trial). See Figure \ref{fig:tdAccount} for how various RCI-ratios are calculated.

\begin{figure} 
\begin{center}
\includegraphics[width = \textwidth]{Images/tdAccount.pdf}
\caption{Various manipulations of temporal distinctiveness as used by \cite{Horoufchin2011, Horoufchin2011a}. Task instances are represented by circles, and time runs from left to right. The current trial's cue is represented by the far-right circle; the episodic trace of the previous task is the middle circle, and the episodic trace of the task from two trials ago is the far-left circle. The RCI between each trace is shown for each row. The ratio is calculated as RCI(n--2:n--1) / RCI(n--1:current trial). See text for more details.}
\label{fig:tdAccount}
\end{center}
\end{figure}

When RCI-ratio is high, so too is TD, which means there is a high probability the episodic trace can be retrieved; successful retrieval \jg{of the task-set} primes performance, leading to a fast RT. When the RCI-ratio is low, so too is TD, which lowers the probability of successful retrieval \jg{of the task-set}. When retrieval fails, the task must be performed via a slower, algorithmic route, leading to a slower RT \citep[see][for a similar proposal]{Logan2002}. Intermediate RCI-ratios lead to intermediate levels of TD; therefore, a proportion of these trials will have successful retrieval, and some trials will have failed retrieval.

Figure \ref{fig:grangeData} represents a portion of data reported by \cite{Grangeinrevision}---a brief overview of the pertinent method details and analysis are presented in Appendix A---that replicates the main findings from \cite{Horoufchin2011a}; focussing on repetition RTs, increasing RCI from 50ms to 1000ms has negligible effect on RTs when the RCI was the same as the previous trial (e.g., these data points relate to D and C in Figure \ref{fig:tdAccount}); this is because both of these conditions have an identical RCI-ratio of 1, and hence have the same TD. RCI has a considerable effect on repetition RT when the RCI has changed from the previous trial: RT is very fast when the RCI is 50ms, as this condition has a very high RCI-ratio, hence high TD (Figure \ref{fig:tdAccount} A); RT is very slow when the RCI is 1000ms, as this condition has a very low RCI-ratio, hence low TD (Figure \ref{fig:tdAccount} B).

% \iftoggle{jou}{
% \begin{figure}
% \begin{center}
% \includegraphics[width = 0.5\textwidth]{Images/grangeData.pdf}
% \caption{Data from \cite{Grangeinrevision} showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial. Error bars denote  +/- 1 standard error around the mean.}
% \label{fig:grangeData}
% \end{center}
% \end{figure}
% }{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/grangeData.pdf}
\caption{Data from \cite{Grangeinrevision} showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial. Error bars denote  +/- 1 standard error around the mean.}
\label{fig:grangeData}
\end{center}
\end{figure}
% }

@@

I approach this assessment in two ways. In the first, I use a statistical test---the fixed-point property test---to assess the presence/absence of evidence for intermediate RCI-ratios being a mixture of a fast and a slow distribution. Then, in a next step I extend the model of \cite{Grange2015} to predict whole RT-distributions, which allows a direct test of the mixture-distribution assumption.

\jg{\subsection{Switch Trials}}
\jg{Note that the current paper does not attempt to model switch RT performance. This is for several reasons. One is that there is evidence that RCI does not affect switch RT \citep{Altmann2005, Horoufchin2011a, Meiran2000a}. Second, the temporal distinctiveness account of \cite{Horoufchin2011a} mostly considers task repetition performance because the RCI-ratio did not influence switch trials. As such, the formal model of \cite{Grange2015} only modelled repetition RTs. As the purpose of the present paper is to test further the main assumptions of the account of \cite{Horoufchin2011a} and the formal model of \cite{Grange2015}, the current work continues to focus on repetition RT. A complete model would of course have to account for switch trial performance, too, but as these trials appear unaffected by temporal distinctiveness they are less interesting for the aims of the current paper. I leave discussion of this issue to the General Discussion.}

%%%--------------------------------------------------------------------------------------------
\section{Assessing the Presence of Mixture-Distributions}
\cite{VanMaanen2014} introduced a method---the ``fixed-point'' property test---for statistically testing the presence of a mixture-distribution. If distribution $z$ is a mixture of two base distributions $x$ and $y$, then the fixed-point property states that the probability density for distribution $z$, $f_{z}$, is a weighted sum of the probability densities of the other two distributions $f_{x}$ and $f_{y}$. Put simply, this implies that there exists a particular response time $t$ for which the probability of providing such a response is identical for all three distributions; that is $f_{x}(t)$ = $f_{z}(t)$ = $f_{y}(t)$.

@@

% \iftoggle{jou}{
% \begin{figure}
% \begin{center}
% \includegraphics[width = 0.5\textwidth]{Images/fpExample.pdf}
% \caption{Example of the fixed-point property in three distributions. Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7. The left panel shows the probability densities for each distribution. The right panel shows the density difference between different density functions. The distributions share a common crossing point at about 0.850 seconds.}
% \label{fig:fpExample}
% \end{center}
% \end{figure}
% }{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/fpExample.pdf}
\caption{Example of the fixed-point property in three distributions. Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7. The left panel shows the probability densities for each distribution. The right panel shows the density difference between different density functions. The distributions share a common crossing point at about 0.850 seconds.}
\label{fig:fpExample}
\end{center}
\end{figure}
% }

@@

%%----------
\subsection{Application to the Data}
The task repetition data from Figure \ref{fig:grangeData} was assessed for the presence of a fixed-point property. In this test, the RCI-ratio of 20 can be considered the ``fast'' distribution, and the RCI-ratio of 0.05 can be considered the ``slow'' distribution. The critical question is whether intermediate RCI-ratios of 1 are a mixture of the fast and the slow distribution. \jg{For this test, I collapsed the 50--50 and 1000--1000 data, as both represent an RCI-ratio of 1. The mean difference between these two conditions was 54.8ms, but was not statistically significant, $t$(24) = 1.7496, $p$ = 0.09. The Bayes factor for this test was $BF_{01}$ = 1.26, which slightly favours the null of no difference (although this is not decisive).}

Data were trimmed before testing. Correct RTs were trimmed to retain RTs slower than 150 milliseconds, and RTs faster than 2.5 standard deviations above each subjects' mean RT. The data was then assessed for the presence of a fixed-point by passing it to the \texttt{fp} function provided in the form of \texttt{R} code from \citet{VanMaanen2014}. \jg{This takes the individual participants' RT data as input.} Visual representation of the fixed-point assessment is shown in Figure \ref{fig:mixtureDistributionData}.

\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/mixtureDistributionData.pdf}
\caption{Test of the fixed-point property in three distributions from \cite{Grangeinrevision}. The left panel shows the individual density functions for each condition of RCI-ratio (1 = 0.05, 2 = 1, 3 = 20). The middle panel shows ``crossing points'': the subtraction of pairs of density functions (indicated in legend). The right panel shows box-plots for the distribution of crossing points for individual participants in the study.}
\label{fig:mixtureDistributionData}
\end{center}
\end{figure}

As shown in the left and center panels of Figure \ref{fig:mixtureDistributionData}, the three \jg{group-averaged} RT distribution functions share a common crossing point at just over 1 second. The right panel of Figure \ref{fig:mixtureDistributionData} shows box-plots of the distribution \jg{across individual participant data} of crossing points for each pair. There is considerable overlap in the box-plots suggesting no difference between condition pairs of crossing point (supporting the fixed-point property). Together, this visual inspection provides good evidence that the RT function for the RCI-ratio of 1 is a weighted mixture of the ``slow'' RT distribution (where RCI-ratio = 0.05) and the ``fast'' RT distribution (where RCI-ratio = 20), as predicted by the temporal distinctiveness model \citep{Grange2015}.

@@

% \iftoggle{jou}{
% \begin{figure}
% \begin{center}
% \includegraphics[width = 0.5 \textwidth]{Images/modelOverview.pdf}
% \caption{Overview of the retrieval processes in the model.}
% \label{fig:modelOverview}
% \end{center}
% \end{figure}
% }{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/modelOverview.pdf}
\caption{Overview of the retrieval processes in the model.}
\label{fig:modelOverview}
\end{center}
\end{figure}
% }

@@

\jg{All modelling was performed on group-averaged data.} \cite{Grange2015} used the full mathematics of SIMPLE to obtain $p$(retrieved). To reduce the number of free parameters, in the current model $p$(retrieved) was treated as a ``semi-fixed'' parameter. To achieve this, the RCI-ratio was calculated for each RCI-sequence condition in Figure \ref{fig:grangeData}. Specifically, the RCI-ratio was 20 for n--2 to n--1 RCIs of 1000ms---50ms; the ratio was 1 for RCIs of 1000ms--1000ms and 50ms--50ms; and the ratio was 0.05 for RCIs of 50ms--1000ms. $p$(retrieved) was ``semi-fixed'' in the sense that it was fixed at $p$(retrieved) = 1 for ratios of 20 (i.e., perfect retrieval) and fixed at $p$(retrieved) = 0 for ratios of 0.05 (i.e., failed retrieval); $p$(retrieved) was free to vary for ratios of 1. Thus, $p$(retrieved) controls the relative contribution of the two RT distributions for intermediate RCI ratios. \jg{It is of course possible that even in the RCI-ratio of 20 some retrieval failures occur (and vice-versa for RCI-ratios of 0.05). However, for the purposes of this modelling work, I use the simplifying assumption described.}

@@

The model was fitted to the data via a version of Quantile Maximum Probability Estimation \citep[QMPE][]{Heathcote2002}, where the model is fit to \jg{observed frequencies between RT quantiles} rather than individual RTs as per maximum likelihood (see Appendix C for details). This method was used due to the relatively low number of trials per subject, and the rather low error rate. The fits of the model to the behavioural data are shown in Figure \ref{fig:modelFit}. The best-fitting parameters are shown in Table \ref{tab:bestParameters}.

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{Best fitting model parameters from the fit routine. Note that $p$(retrieved) refers to the probability of sampling from the fast distribution only for ratio = 1 data points. See text for details.}
    \begin{tabular}{rr}
    \toprule
    Model Parameter & Value \\
    \midrule
    $p(retrieved)$     & 0.759 \\
    $A$     & 718.14 \\
    $b_{Fast}$ & 114.58 \\
    $b_{Slow}$ & 179.96 \\
    $v_{Fast}$ & 1.132 \\
    $v_{Slow}$ & 0.893 \\
    $s$     & 0.44 \\
    $ter$   & 346.42 \\
    \bottomrule
    \end{tabular}
  \label{tab:bestParameters}
\end{table}

\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/qmp2RCI_drift_+_b.pdf}
\caption{Defective cumulative distribution functions for the behavioural data and the model fit for all RCI-ratios (0.05, 1, \& 20) for correct and error RT distributions.}
\label{fig:modelFit}
\end{center}
\end{figure}

This Figure presents so-called ``defective'' cumulative distribution functions (CDFs). The data are sorted from fastest to slowest, and then quantile cut-off points are calculated for each subject according to a pre-specified set of quantiles $\vec{Q}$ (here $\vec{Q}$ = 0.1, 0.3, 0.5, 0.7, 0.9). The Figure plots the average RT for each quantile across subjects against the quantile value. The plot is a defective CDF in the sense that it also displays information about errors. Specifically, RT is plotted against $\vec{Q}$ $\times$ mean accuracy rather than just $\vec{Q}$. \jg{Perfect accuracy would thus be plotting RT against $\vec{Q}$.} Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{Q}$ $\times$ (1 - mean accuracy).

\jg{The overall fit statistic of the model was QMPE = 330.12. The model fit to correct RT distributions is rather good; the model's prediction for mean RT gave $R^{2}$ = 0.986.} The model captures all of the main trends in the data: RT becomes facilitated as $p$(retrieved) increases (from left-to-right $p$(retrieved) = 0, $p$(retrieved) = 0.759, and $p$(retrieved) = 1). This improvement in RT is largely at the slower end of the RT distribution. Also, \jg{the height of the defective CDFs increases as $p$(retrieved) is increased}, reflecting generally better accuracy. Importantly, the central plot shows a good fit of the model to the data, providing support that intermediate TDs are a mixture of two base distributions.

The fit to the error RT distributions is not as good as for the correct RT distributions; \jg{the model's prediction for mean RT gave $R^{2}$ = 0.864.} However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 80\% accuracy, and average accuracy was much higher). So, there were often few error RTs per quantile bin during the model fit, making accurate estimation difficult. However, despite the poor quantitative fit, the qualitative pattern seen in the behavioural data is generally reproduced: error RT becomes generally faster and less variable as ratio increases.

@@

\section{Conclusion}
The present paper sought to assess the evidence in favour of a key prediction of the TD hypothesis of RCI effects on task repetition trials in task switching, namely that repetition RTs are a mixture of only one of two processes. In sum, this paper has provided good support for the TD prediction, which provides more support for these theoretical accounts \citep{Grange2015, Horoufchin2011, Horoufchin2011a}. This presents an important challenge to models of cognitive control during task switching which assume control systems work to prevent relevant task-sets decaying. Instead, loss of retrieval of task-sets appears to be well-explained by interference effects rather than time-based decay.

@@

%%%--------------------------------------------------------------------------------------------
\appendix
\section{Method and Results \citep{Grangeinrevision}}
The data presented in Figure \ref{fig:grangeData} presents a portion of the overall data presented by \cite{Grangeinrevision}. Speficially, this data comes from the ``categorisation'' condition. In this condition, 25 participants were presented with a 2x2 square grid. Two arrow cues either pointed up and down (presented above and below the grid, respectively) or left and right (presented to the left and to the right of the grid, respectively). 100ms later, a stimulus appeared in one of the grid's cells. The stimulus could be an A or a 4, presented in either red or blue font. If the arrows pointed up and down, the participants had to judge whether the stimulus was an A or a 4; if the arrows pointed left and right, the participants had to judge whether the stimulus was red or blue. Participants responded using the ``1'' and the ``9'' keys on the numerical part of the keyboard; 1 corresponded to ``letter'' and ``red'' responses, and 9 corresponded to ``number'' and ``blue'' responses. Once a response was registered, the grid was cleared for an RCI of either 50ms or 1000ms (chosen randomly). The next task was chosen randomly. In total, participants were presented with 6 blocks of 64 trials, preceded by 16 practice trials.

@@

As we are only considering the similarity between two items ($i$ and $j$), and as an item's similarity to itself is 1, Equation \ref{eq:simpleDiscriminationA} becomes

\begin{equation}
D_{i} = \frac{1}{\eta_{ij} + 1}.
\label{eq:simpleDiscriminationB}
\end{equation}
